Pillar 1 - Sequential Pattern Mining

### 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
experiment with transcipts and enquo

d_sequence_transactions <- d_course %>%

@@

```
#Condensing grade

@@

>>>>

#this is new-----
transcript_to_use <- quo(distributed_transcript) #d_transcript or distributed_transcript 
#----------------
d_sequence_transactions <- d_course %>%

@@

```
#puting everything into quasi-function

@@

#parameters for analysis
category <-quo(Low_grade) #Outcome or Low_grade or Discrete_grade or #None
transcript_to_use <- quo(distributed_transcript) #d_transcript or distributed_transcript 
fail_threshold <- 6.5

#Preparing data
d_sequence_transactions <- d_course %>%

  left_join(!!transcript_to_use, by = "Course ID") %>%
  mutate(
    Outcome = 
           case_when( Grade == -1   ~"Fail", #if we don't do this NG satisfies the condition for pass v
                      Grade  > 5.5 ~"Pass",
                               T~"Fail"),
    Low_grade =
           case_when(Grade == -1 ~"low score", #if we don't do this NG satisfies the condition for pass v
                      Grade > fail_threshold ~"high score",
                               T~"low score"),
    Discrete_grade =
           case_when(Grade <= 5.4             ~ 5.0,
                     between(Grade, 5.5, 6.4) ~ 6.0,
                     between(Grade, 6.5, 7.4) ~ 7.0,
                     between(Grade, 7.5, 8.4) ~ 8.0,
                     between(Grade, 8.5, 9.4) ~ 9.0,
                     Grade >= 9.5             ~ 10.0,
                     T ~ -99999    #this is a control, we should not have any grades here
                     ),
    None= "" # this might not be optimal
         ) %>%
